\documentclass[letterpaper]{article} % Feel free to change this
\usepackage{graphicx}
\graphicspath{{images/}}
\begin{document}


\title{ECE 350: Digital Systems Homework 7}
\author{Your Name} % Change this to your name
\date{\today} % Change this to the date you are submitting
\maketitle

\section*{Duke Community Standard}

By submitting this \LaTeX{} document, I affirm that
\begin{enumerate}
    \item I understand that each \texttt{git} commit I create in this repository is a submission.
    \item I affirm that each submission complies with the Duke Community Standard and the guidelines set forth for this assignment.
    \item I further acknowledge that any content not included in this commit under the version control system cannot be considered as a part of my submission.
    \item Finally, I understand that a submission is considered submitted when it has been received by the server.
\end{enumerate}

\newpage

\section{Project Design}


The overall idea for our project is to use two FPGA boards in order to implement a web server. One FPGA board acts as a client and uses input buttons to send requests to retrieve web pages. These requests are sent along an ethernet cable to a separate FPGA board. Once the other board, which acts as a web server, receives a request, it sends back an appropriate web page along an ethernet cable to the original FPGA client board. Once the original FPGA board receives the raw web page data, it decodes the data and then parses it. The data is structured as a custom subset of HTML. Once it finishes parsing the data, the FPGA board renders the data as appropriate on the VGA monitor.
